A large-scale analysis of racial disparities in police stops across the

### 2019-07-29 lib/paper_results.Rmd
Update to match paper text

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  group_by(subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

@@

>>>>

Number of state patrols with data for search analysis: 
`r pfs$rates$search %>% filter(city == "Statewide") %>% select(state) %>% n_distinct`
Number of city departments with data for search analysis: 
`r pfs$rates$search %>% filter(city != "Statewide") %>% select(state, city) %>% n_distinct`

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

@@

Number of robustness check models with results not statistically significant: 
`r vod$dst %>% filter(is_dark + 1.96*std_error >= 0) %>% nrow`
